Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-04-07 ms.tex
Adding subsections

@@

@@

\begin{figure}
    \centering
    \includegraphics{pdf_xinit0.0.pdf}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$. Photons are initialized with $\rm x = 0.0$. In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.} 
    \label{fig:sol_mc_residual_0}
\end{figure}

@@

For each numerical solution, the monochromatic source of photons was initialized with a different starting frequency to evaluate the analytic solutions' accuracy with variation of the parameter $\rm \sigma_s$. This is related to $\rm x_{init}$ by 
\begin{equation} \label{sigma0_xinit}
    \sigma_0 = \frac{\beta}{a} \rm x_{init}^3
\end{equation}

where $\beta = \sqrt{2 \pi / 27}$. Monte Carlo numerical simulations were performed with $\rm x_{init} = (0.0, 2.0, 4.0 ... 12.0)$ and optical depths $\tau_0 = (10^6, 10^7)$. In Fig. \ref{fig:sol_mc_residual_0}, \ref{fig:sol_mc_residual_6} and \ref{fig:sol_mc_residual_12}, these are compared with the analytic solutions at selected initial frequencies. In each of these figures, the contribution of the flux from Eq. \ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$. The corrected solution, $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing. It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings. The $H_{\rm bc}$ correction term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, produces a successful analytical result that characterizes the probability distribution of frequencies for escaping photons, including situations in which the photons are given initial frequencies outside of the line core.

@@

\section{ time-dependent diffusion }

@@

@@

@@

It is expected that the time-integrated spectrum of the response to an impulse will agree well with the time-independent spectrum. We first evaluate the time-dependent response using our eigenfrequency sweeping method. Once the probabilities $P_{nm}(\sigma)$ are calculated as above, the escape time distributions for all photon frequencies are calculated by summing over the frequency eigenfunctions $P_{nm} \exp(s_{nm}t)$. Integrating $P_{nm}$ with respect to $t$, we obtain

\be
\int 
\ee

>>>>

\subsection{Background}
\label{subsec:no_destruction:background}

@@

\subsection{Equations}
\label{subsec:no_destruction:equations}

@@

\subsection{Numerical Methods}
\label{subsec:no_destruction:methods}
For each numerical solution, the monochromatic source of photons was initialized with a different starting frequency to evaluate the analytic solutions' accuracy with variation of the parameter $\rm \sigma_s$. This is related to $\rm x_{init}$ by 
\begin{equation} \label{sigma0_xinit}
    \sigma_0 = \frac{\beta}{a} \rm x_{init}^3
\end{equation}

where $\beta = \sqrt{2 \pi / 27}$. Monte Carlo numerical simulations were performed with $\rm x_{init} = (0.0, 2.0, 4.0 ... 12.0)$ and optical depths $\tau_0 = (10^6, 10^7)$.

\subsection{Results}
\label{subsec:no_destruction:results}
\begin{figure}
    \centering
    \includegraphics{pdf_xinit0.0.pdf}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$. Photons are initialized with $\rm x = 0.0$. In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.} 
    \label{fig:sol_mc_residual_0}
\end{figure}

@@

 In Fig. \ref{fig:sol_mc_residual_0}, \ref{fig:sol_mc_residual_6} and \ref{fig:sol_mc_residual_12}, these are compared with the analytic solutions at selected initial frequencies. In each of these figures, the contribution of the flux from Eq. \ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$. The corrected solution, $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing. It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings. The $H_{\rm bc}$ correction term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, produces a successful analytical result that characterizes the probability distribution of frequencies for escaping photons, including situations in which the photons are given initial frequencies outside of the line core.

@@

\section{Time-Dependent Diffusion}
\label{sec:time_dependent}

\subsection{Background}
\label{subsec:time_dependent:background}

@@

\subsection{Equations}
\label{subsec:time_dependent:equations}

@@

\subsection{Numerical Methods}
\label{subsec:time_dependent:numerical_methods}

@@

It is expected that the time-integrated spectrum of the response to an impulse will agree well with the solution for the steady-state spectrum (Eq. TODO: Steady state eqn). We first evaluate the time-dependent response using our eigenfrequency sweeping method. Once the probabilities $P_{nm}(\sigma)$ are calculated as above, the escape time distributions for all photon frequencies are calculated by summing over the frequency eigenfunctions $P_{nm} \exp(s_{nm}t)$. Integrating $P_{nm}$ with respect to $t$, we obtain

\subsection{Results}
\label{subsec:time_dependent:results}
